% Intro/Purpose
The purpose of the Python program is to calculate the distance and angle between
two points on Earth's surface. The program does this by offering two functions;
one can convert the degrees-minutes-seconds(dms) that longitude and latitude are
typically represented in into decimal degrees. And a second function that can
take two points in decimal longitude and latitude and calculate the distance and
angle between the two points. Thus the two functions can easily be used to
convert longitude and latitude acquired from a map or GPS into a distance and
angle.

% Coding process
The program was written by breaking down the goal into smaller and smaller
components until it was trivial to implement. Each component was written as its
own function that could be called by each other to be formed into the final
function. For example function one calls a function to get the user's input and
then passes that input to a function that converts the dms angle into a decimal
angle. Then it prints out the converted angle in a nice, human friendly
way. Coding this way was quite simple since each function was either simple
enough to code directly or complex enough to be split into simpler functions
that were then considered.

% Overall structure
The program's overall structure is quite simple. Program execution begins in a
loop, where the user is prompted to select from a menu. Selected option one or two
executes function one or two before finishing the loop. The loop will repeat as
long as the user does not select option three from the menu; continiously
prompting for a selection and executing a function if selected.

% Function 1 dms -> decimal
